Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-19 Draft.Rmd
Update Draft.Rmd

# Check  lin. regr. model performance using cross-validation
folds1 <- vfold_cv(train, v = 10)
folds1
res1 <- fit_resamples(wf1, resamples = folds1)
res1 %>% 
    collect_metrics()
```

>>>>

# Check  lin. regr. model performance using cross-validation
folds1 <- vfold_cv(train, v = 10)
folds1
res1 <- fit_resamples(wf1, resamples = folds1)
res1 %>% 
    collect_metrics()
```
```{r kNN}
## Scale the data for k-NN model
origin_scaled <- origin %>% 
    mutate(across(-value, scale))

## Create the model
model2 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("classification")

## Create workflow
  wf2 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model2)

## Fit the model on the full training dataset using the `fit()` function
pokemon_kNN <- fit(wf2, data = train)

## Check performance on the complete training data
res2 %>% 
    extract_fit_engine() %>% 
    summary()

## Check performance using cross-validation
folds <- vfold_cv(train, v = 10)
folds
res2 <- fit_resamples(wf2, resamples = folds)
res2 %>% 
    collect_metrics()
```

```{r Bootstrap}
## Create Bootstrap Model
model3 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("classification")

## Create workflow
  wf3 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model3)

```{r Random Forests}
## Create Random Forest Model
model4 <- rand_forest(mtry = 5) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")

## Create workflow
  wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model4)
